### 2015-07-13 cover-collab.tex
substantial changes to intro and particularly the application use case
added additional Sandia computing resources

\noindent
{\bf Description of facilities, equipment, and resources}: We summarize these here; detailed information is provided in the supplementary documents.
\begin{itemize}
\item
{\bf Oak Ridge National Laboratory}. \underline{Computers}:
Oak Ridge Leadership Facility (discretionary time for SNS experiments), including
Titan, Gaea (a Cray XE6 system), the ORNL Institutional Cluster (OIC),
and Frost. A cloud resource, CADES, can be made available to
researchers in this project, as well as the sith cluster which has a Lustre file
sysem, 2 SSD on each node, and access to the cneter wide Spider file system.
 \underline{Networks}: 100 Gbps connection to ESnet.
\vspace{-1ex}
\item
{\bf Rutgers University}. \underline{Computers}: Excalibur BGP, Clusters, CometCloud, and CAPER testbeds. \underline{Networks}: 10 Gbps to Internet2.
\vspace{-1ex}
\item
{\bf Sandia National Laboratory}.
\underline{Computers}: 264 TF Red Sky system and many testbed systems
\underline{Networks}: 100 Gbps to ESnet
\item
{\bf UCSC}.
\underline{Computers}:  48 node system and access to the ISSDM storage resource
\underline{Networks}: 1 Gbps to ESnet

\end{itemize}

@@

>>>>

\noindent
{\bf Description of facilities, equipment, and resources}: We summarize these here; detailed information is provided in the supplementary documents.
\begin{itemize}[itemsep=1pt,topsep=2pt]
\item
{\bf Oak Ridge National Laboratory}. \underline{Computers}:
Oak Ridge Leadership Facility (discretionary time for SNS experiments), including
Titan, Gaea (a Cray XE6 system), the ORNL Institutional Cluster (OIC),
and Frost. A cloud resource, CADES, can be made available to
researchers in this project, as well as the sith cluster which has a Lustre file
sysem, 2 SSD on each node, and access to the cneter wide Spider file system.
 \underline{Networks}: 100 Gbps connection to ESnet.
\vspace{-1ex}
\item
{\bf Rutgers University}. \underline{Computers}: Excalibur BGP, Clusters, CometCloud, and CAPER testbeds. \underline{Networks}: 10 Gbps to Internet2.
\vspace{-1ex}
\item
{\bf Sandia National Laboratory}.
\underline{Computers}: 1.1 PF Cielo, {\textasciitilde}40 PF Trinity, 264 TF Red Sky system and many testbed systems.
\underline{Networks}: 100 Gbps to ESnet.
\item
{\bf University of California Santa-Cruz}.
\underline{Computers}:  48 node system and access to the ISSDM storage resource.
\underline{Networks}: 1 Gbps to ESnet.
\end{itemize}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proposal"
%%% End:
